---
title: "McNinch_Review_For_Shook"
author: "Colton McNinch"
date: "10/17/2017"
output: pdf_document
---

I will attempt to highlight any segments of code I felt needed brushed up on below. Overall, I would rate this code as good and realatively straightforward. There was not a `Data Inspection` portion yet and can hopefully be added. The `Data Processing` section was 
quite good. The `Part II` or graphing portions were fine, however I ran into some
problems where the `cbind` function didn't work because the two vectors being bound
were not of the same length. This effectively hindered me from continuing. Hopefully 
that section can be made more robust. 


In this code section, the resulting data frame is correct. However, if 
one were to want to know which columns went with which individuals (i.e. Sample_ID) it might 
be beneficial to capture those sample names as a character vector (simply the first row
of the `transposed_maize` data frame) and then assign those to the appropriate 
column names of the merged_maize data frame 
```{r}
##Join SNP data to genotypes data
merged_maize <- merge(snps, transposed_maize, by.x = "SNP_ID", by.y = "row.names")
```


In this code section, you need to add `.txt` to the end of 
`"maize_chromosome_%d_decreasing_snps"` so that the resulting files can be accessed. 
``` {r}
##Make files for each chromosome

for (i in 1:10) {
  maize_loop <- maize_dashes[maize_dashes$Chromosome == i,]
  write.csv(maize_loop, sprintf("maize_chromosome_%d_decreasing_snps", i), row.names = F)
}
```



In this code section, I was unable to run `colnames(all_groups) <- colnames(combined)`
because `all_groups` and `combined` did not have the same number of rows this unfortunately 
inhibited me from running all subsequent portions of code. 
```{r}
##Formatting SNPs

snps_2 <- snps[,c(1,3,4)]
combined <- combined[order(combined[,2], combined[,3]),]
row.names(combined) <- seq(1,nrow(combined),1)
all_groups <- all_groups[-1]#formatting for future rbind
all_groups <- cbind(0,0,0,all_groups)
colnames(all_groups) <- colnames(combined)
combined <- rbind(all_groups, combined) #making group info a row, for a later loop
row.names(combined) <- seq(1,nrow(combined),1)
groups <- as.character(unique(fang$Group))

```







